\documentclass[12pt, a4paper, titlepage]{article}

\title{Software Requirements Specification \\ 
\large ParkingAutomation Server}
\author{Rolan Akhmedov \\ GlobalLogic Ukraine, Inc. \\ rolan.kharkiv@gmail.com }
	% use \and to add one more auther
	% \and AUTHER_NAME \\ AUTHER_COMP \\ AUTHER_CONTACT }
\date{\today} 
% use \date{25.12.00} to set specific date

\usepackage{indentfirst} % intend first passage in the section

\begin{document}
	\maketitle
	
	% \begin{abstract} \end{abstract}
	
	\section{Introduction}
		ParkingAutomation is a server software for traffic monitoring on a parking area.
		It contains computer vision server and a client (server utilities). 
		The server manages life parking information form IP cameras;
		The utilities impact allows to control a recognition process and the output.
		The output management is relied on web server but the utilities provides
		an access to a database entity and video strimming threads.
		\par 
		Client-server communication is implemented though a IPC socket schema.
		Server performs traffic and system log so any log event can be sent like a
		notification through MQ, IM, SIP, e-mail, etc. 
		Notification handling is not coved by the server scope.

	\section{Overall description}
		\subsection{Product perspective}
			\begin{itemize}
				\item System Interfaces \\ Parking Object Interface Description
				\item User and Communication Interfaces \\ CLI, text output
				\item Software interfaces \\ rtfs:// stream
				\item Memory Constraints \\ Min RAM \& Min Disk Space Value
			\end{itemize}
		\subsection{Product functions}
			\begin{enumerate}
				\item Spot status recognition
				\begin{enumerate}
					\item status update one time the minute
					\item \ldots
				\end{enumerate}
				\item Traffic monitoring
				\begin{enumerate}
					\item \ldots
				\end{enumerate}	
				\item Accident notification
				\begin{enumerate}
					\item \ldots
				\end{enumerate}	 
				\item System control
				\begin{enumerate}
					\item \ldots
				\end{enumerate}	
			\end{enumerate}
		\subsection{Constraints, assumptions and dependencies}
			
		
	\section{Specific requirements}
		\subsection{External interface requirements}
			SQL Database
			
		\subsection{Functional requirements}
			Does it different form Product functions?
			
		\subsection{Performance requirements}
			Is duplication allowed?
			
		\subsection{Design constraints}
			\begin{itemize}
				\item Must allow to add new recognition method
				\item \ldots
			\end{itemize}
			
		\subsection{Software System attributes}
			\begin{itemize}
				\item Reliability \\ Hardware exaction handling is required
				\item Security \\ Config contains camera access
				\item Maintainability \\ Makefile
				\item Portability \\ Windows, Linux
			\end{itemize}


\end{document}
